Random Forests

### 2020-07-02 pkg/partykit/inst/ULGcourse-2020/slides_forest.Rnw
small corrections in formula notations
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3031 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: ac8ccb92d32857780505b5b302a34c35ef883e34

\visible<13->{
for $\hat{y}_t$ being the average response value in the corresponding segment $\mathcal{B}^t_x$ of the $t$-th tree for learning data $\{y_i\}_{i=1,\ldots,n}$:

@@

\begin{frame}
\frametitle{Aggregation of trees}
{\bf Simple tree model:} Obtain predictions for the response $y$ by averaging over observations in the same terminal node $\mathcal{B}_x$: 
$$
\hat{y}= \frac{1}{|\mathcal{B}_x|} \sum_{i: y_i \in \mathcal{B}_x} y_i
\visible<2->{
\ =\ \sum_{i=1}^n w_i(x) \cdot y_i$$
}

{\bf Model-based tree:} Obtain predictions for model parameter(s) $\theta$ by optimizing an objective function $f$ for all observations in the same terminal node $\mathcal{B}_x$:
$$
\hat{\theta}= \argmin_{\theta} \sum_{i: y_i \in \mathcal{B}_x} f(\theta; y_i)
\visible<2->{
\ =\ \argmin_{\theta} \sum_{i=1}^n w_i(x) \cdot f(\theta; y_i)$$
}

{\bf Note:} The model-based approach allows for fitting complex models but also includes the specific case of averaging over all observations which corresponds to minimizing the residual sum of squares $\sum (Y - \hat{Y})^2$.

@@

The predicted model parameter (vector) $\hat{\theta}$ 
is the argument of the parameter space $\Theta$ 
that minimizes the weighted sum of the objective function $f$ evaluated for learning data $\{y_i\}_{i=1,\ldots,n}$:

>>>>

\visible<13->{
for $\hat{y}_t$ being the average response value in the segment $\mathcal{B}^t_x$ which the observed covariate $x$ is assigned to in the $t$-th tree with learning data $\{(y_i,x_i)\}_{i=1,\ldots,n}$:

@@

\begin{frame}
\frametitle{Aggregation of trees}
{\bf Simple tree model:} Obtain the predicted response $\hat{y}$ for an observed covariate~$x$ by averaging over observations in the same terminal node $\mathcal{B}_x$: 
$$
\hat{y}= \frac{1}{|\mathcal{B}_x|} \sum_{i: y_i \in \mathcal{B}_x} y_i
\visible<2->{
\ =\ \sum_{i=1}^n w_i(x) \cdot y_i$$
}

{\bf Model-based tree:} Obtain the predicted model parameter(s) $\hat{\theta}$ for an observed covariate~$x$ by optimizing an objective function $f$ for all observations in the same terminal node $\mathcal{B}_x$:
$$
\hat{\theta}= \argmin_{\theta} \sum_{i: y_i \in \mathcal{B}_x} f(\theta; y_i)
\visible<2->{
\ =\ \argmin_{\theta} \sum_{i=1}^n w_i(x) \cdot f(\theta; y_i)$$
}

{\bf Note:} The model-based approach allows for fitting complex models but also includes the specific case of averaging over all observations which corresponds to minimizing the residual sum of squares $\sum (y_i - \theta)^2$.

@@

The predicted model parameter (vector) $\hat{\theta}$ 
is the argument of the parameter space $\Theta$ 
that minimizes the weighted sum of the objective function $f$ evaluated for learning data $\{(y_i,x_i)\}_{i=1,\ldots,n}$:
